Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores. II. Nanoflare Trains

### 2016-10-13 tex/paper.tex
minor paper updates

%Define new commands as needed
\newcommand{\ang}{\AA~}
\defcitealias{barnes_inference_2016-1}{Paper I}
\renewcommand{\sectionautorefname}{Section}
\renewcommand{\subsectionautorefname}{Subsection}
%Set tikz options
\tikzstyle{box} = [rectangle, rounded corners, text centered, draw=black]
\tikzstyle{ghost} = [rectangle, rounded corners, text centered, draw=white]
\tikzstyle{arrow} = [thick, ->, >=stealth]

@@

	\par An analogous approach can be used to investigate the properties of the ``hot" coronal component expected from nanoflare heating, and is the subject of the present series of papers. In \citet{barnes_inference_2016-1} \citepalias[hereafter]{barnes_inference_2016-1}, we looked at the hot plasma properties due to a single isolated nanoflare. The effects of heating pulse duration, changes to conductive cooling due to heat flux limiting, differential heating of electrons and ions, and non-equilibrium ionization (NEI) were studied. It was shown that signatures of nanoflare heating are likely to be found in the temperature range $4\lesssim T\lesssim 10$ MK. The prospect of measurable signatures above $10$ MK was found to be diminished for short heating pulses (with duration $<100$ s), NEI, and differential heating of the ions rather than the electrons. It is important to stress for a single nanoflare that while the ``hot'' plasma is present, it cannot actually be detected.

@@

	\par In order to treat the evolution of the electron and ion populations separately, we use a modified version of the usual EBTEL equations. This amounts to computing spatial averages of the two-fluid hydrodynamic equations over both the transition region and corona. A full description and derivation of these equations can be found in Appendix B of \citetalias{barnes_inference_2016-1}. The relevant two-fluid pressure and density equations are,

@@

	where $c_2=\bar{T}_e/T_{e,a}\approx0.9$, $c_3=T_{e,0}/T_{e,a}\approx0.6$, $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency, and $\psi_{TR}$ is a term included to maintain charge and current and neutrality. Additionally, $c_1=\mathcal{R}_{TR}/\mathcal{R}_C$ and its formulation is discussed in \citet{cargill_enthalpy-based_2012} with additional modifications detailed in Appendix A of \citetalias{barnes_inference_2016-1}. These equations are closed by the equations of state $p_e=k_BnT_e$ and $p_i=k_BnT_i$. In the cases where we treat the plasma as a single-fluid, we use the original EBTEL model as described in \citet{klimchuk_highly_2008,cargill_enthalpy-based_2012}.

@@

	\par The loop is heated by a prescribed heating function, applied to either the electrons ($\bar{Q}_e$) or the ions ($\bar{Q}_i$). Both species cool through a combination of thermal conduction ($F_{ce,0},\,F_{ci,0}$) and an enthalpy flux to the lower atmosphere, with the electrons also undergoing radiative cooling ($\mathcal{R_C}$). In the case of conductive cooling, a flux limiter, $F_s=(1/2)fnk_BTV_e$, is imposed to mitigate runaway cooling in a low-density, high-temperature plasma. In all cases we use a saturation limit of $f=1$. See \citetalias{barnes_inference_2016-1} for a discussion of how $f$ is likely to effect the presence of hot emission in a nanoflare-heated plasma.

@@

	\par When considering the role of nanoflares in the production of hot plasma in AR cores, it is important to take non-equilibrium ionization (NEI) into account \citep{bradshaw_explosive_2006,reale_nonequilibrium_2008,barnes_inference_2016-1}. In a steady heating scenario, the ionization state is an adequate measure of the electron plasma temperature. Because the heating timescale is long (effectively infinite), the ionization state has plenty of time to come into equilibrium with the electron temperature. 

@@

	\par As in \citetalias{barnes_inference_2016-1}, we use the numerical code\footnote{This code has been made freely available by the author and can be downloaded at: \url{https://github.com/rice-solar-physics/IonPopSolver}.} outlined in \citet{bradshaw_numerical_2009} to asses the impact of NEI on our results. Given a temperature and density profile from EBTEL, we compute the non-equilibrium ionization states for Fe IX through XXVII and the corresponding effective electron temperature, $T_{eff}$, that would be inferred by assuming ionization equilibrium. Using $T_{eff}$, we are then able to compute a corresponding NEI emission measure distribution, $\mathrm{EM}(T_{eff})$.

@@

	\par We now show the results of our nanoflare train simulations for each point in our multidimensional parameter space: species heated (single-fluid, electron or ion), power-law index ($\alpha$), waiting time ($t_N$), and waiting-time/event energy relationship ($\beta$). In each 0D hydrodynamic simulation, a loop of half-length $L=40$ Mm is heated by $N$ triangular events of duration $\tau=200$ s and peak heating rate $H_i$ for a duration of $t_{total}=8\times10^4$ s. The average interval between subsequent events is $t_N$ (in the uniform and $\beta=0$ cases, $t_{N,i}=t_N$ exactly for all $i$). We focus primarily on the emission measure distribution, $\mathrm{EM}(T)$, and observables typically calculated from $\mathrm{EM}(T)$. In all cases, the coronal emission measure is calculated according to the method outlined in section 3 of \citetalias{barnes_inference_2016-1}. The corresponding NEI results, $\mathrm{EM}(T_{eff})$, are calculated similarly, but using $T_{eff}$ (see \autoref{subsec:nei}) instead of $T$. 

@@

	\par We compare $\mathrm{EM}(T)$ for three different types of heating functions, across a sample of six different heating frequencies. \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} show the emission measure distributions for the single-fluid, electron heating, and ion heating cases respectively. Each panel corresponds to a different average waiting time ($t_N$) and includes three different types of heating functions: uniform heating events (red), events chosen from a single power-law distribution of index $\alpha=-2.5$ with constant waiting time ($\beta=0$ case, blue), and a waiting time that depends on the energy released in the preceding event ($\beta=1$ case, green). The dashed lines denote the corresponding NEI cases, $\mathrm{EM}(T_{eff})$. The cases shown in \citetalias{barnes_inference_2016-1} correspond approximately to the red curves in the lower right panels ($t_N=5000$ s) in each of the three figures since the loop is allowed to cool and drain completely before reheating and a single nanoflare energy is used. 

@@

	\par The behavior of $\mathrm{EM}(T)$ above $T_m$ is more complicated, but because $\mathrm{EM}(T_m)$ and $T_m$ are the same for all parameters, we can make a meaningful comparison between the different heating models. For the single-fluid model and short $t_N$, the emission measure distribution falls off sharply on the hot side for a uniform nanoflare train, but choosing heating events from a power law leads to a broader distribution. This just reflects the different initial temperatures generated with a power-law distribution since $T \simeq H^{2/7}$, where $H$ is the heating rate. As $t_N$ increases, the distribution for uniform heating gradually broadens as the initial temperature rises due to the lower density in which the heating occurs. A similar broadening occurs for power law heating distributions with the $\beta=0$ and $\beta=1$ results showing little difference. Note that the $\beta=0$ curve is barely visible as it overlaps almost completely with the $\beta=1$ curve. Especially interesting in this case are the results with NEI included. For a uniform nanoflare train, NEI plays no role up to $t_N$ = 2500 sec, but above that it restricts the temperatures that can be detected, as shown in \citetalias{barnes_inference_2016-1}. This hot emission is relocated to cooler temperatures, resulting in a small ``bump'' in the emission measure distribution near 10 MK. On the other hand, NEI plays almost no role in the power-law distributions, for either the $\beta=0$ or $\beta=1$ cases.

@@

	\par When only the ions are heated (\autoref{fig:ion_em}), for intermediate to low heating frequencies (i.e. $t_N\ge1500$ s), $\mathrm{EM}(T)$ in the uniform heating case is truncated below 10 MK and in the power law cases extends to just above 10 MK for the longest waiting time ($t_N=5000$ s). This cutoff at lower temperatures is due to the fact that the electrons cannot ``see'' the ions until they have cooled well below their peak temperature. This is discussed in \citetalias{barnes_inference_2016-1} though in the single-pulse cases, the cutoff occured at lower temperatures. Additionally, in both the uniform and power law cases, the peak of $\mathrm{EM}(T)$ is wider for these low frequencies compared to those shown in the lower right panels of \autoref{fig:single_em} and \autoref{fig:el_em}. NEI now plays no role in any of the cases.

@@

	\par In \citet{cargill_active_2014}, \citetalias{barnes_inference_2016-1}, and \autoref{subsec:em_dist}, we have suggested that the plasma density prior to the nanoflare occuring is a crucial parameter in determining the emission measure distribution. This arises in two distinct ways. Below $T_m$, the temperature and density at which the nanoflare occurs cuts off the emission at lower temperatures. When combined with an energy-dependent waiting time, this can lead to a range of EM slopes in this region \citep{cargill_active_2014}. Above $T_m$, the initial density determines the temperature increase due to the nanoflare, how quickly the initial hot plasma cools, and whether NEI effects are important. We now examine this further.

@@

	\par Our results here suggest that while $a$ is an adequate parameter for describing the cool side of $\mathrm{EM}(T)$, the functional form $\mathrm{EM}\sim T^{-b}$ does not adequately capture the character of the hot part of $\mathrm{EM}(T)$ over any reasonable temperature range. \citet{antiochos_evaporative_1978} showed analytically that accounting for evaporative cooling and assuming constant pressure gives $b=11/2$, though this value can be as low as $b=5/2$ if a flux limiter is included. However, in \citetalias{barnes_inference_2016-1}, we showed that in the case of a single 200 s nanoflare that heats only the electrons, the assumption of constant electron pressure during the heating and early conductive cooling phases does not hold. Our results here are consistent with our findings in \citetalias{barnes_inference_2016-1} in that the parameter $b$ does not provide any valuable information about $\mathrm{EM}(T)$ for $T>T_m$ when two-fluid effects are considered. Clearly, an alternative metric for measuring the amount of hot plasma in the emission measure distribution is needed. 

@@

@@

		\par\citet{brosius_pervasive_2014} proposed another possible diagnostic for the hot non-flaring corona. Using observations of an active region from the \textit{EUNIS-13} sounding rocket, they found that the intensity ratio of Fe XIX (formed at $T\approx10^{6.95}$ K) to Fe XII (formed at $T\approx10^{6.2}$ K) is $\sim0.59$ inside the AR core as compared to $\sim0.076$ outside. They argue that this provides possible evidence for impulsive heating. This arises from the fact that the $\mathrm{EM}(T)$ distribution resulting from low- and intermediate-frequency nanoflares is dual-valued as a function of temperature \citep[see \autoref{fig:single_em}-\autoref{fig:ion_em} and][]{cargill_implications_1994}. For example, in the lower right panel of \autoref{fig:single_em}, $\mathrm{EM}\approx 10^{26.5}$ cm$^{-5}$ at $T = 10^{6.2}$ K and $10^{6.9}$ K. This suggests that the approach of \citet{brosius_pervasive_2014} could be used for any pair of appropriate emission lines and is likely to be of particular use where very limited spectral coverage is available either above or below $T_m$. Indeed for impulsive heating of any kind, the generic $\mathrm{EM}(T)$ curve remains similar (though not identical) as the magnitude of the heating changes. For flare-like energy release one would expect the hot emission to be much greater than the cold emission, with the opposite in the quiet Sun.

	\par We define a general emission measure ratio, $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$ and for this paper consider $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.2}$ K, consistent with \citet{brosius_pervasive_2014}. This also provides a way to compare in a concise way every point in our multidimensional parameter space though we acknowledge that we are reducing $8\times10^4$ s of loop evolution to a single value. This ratio is shown in \autoref{fig:em_ratio_hist_single}, \autoref{fig:em_ratio_hist_el}, and \autoref{fig:em_ratio_hist_ion} for the single-fluid model, electron and ion heating, respectively. In the left-hand panels each individual histogram (denoted by linestyle and color) corresponds to a different type of heating function. This means, for example, that the solid blue histogram includes emission measure ratios for all values of $t_N$, but for only those cases where heating events are chosen from a power-law distribution of $\alpha=-1.5$ and $t_{N,i}=t_N$ for all $i$ (i.e. $\beta=0$). The right panels show these same emission measure ratios, but now categorized by $t_N$. For example, the solid red histogram includes emission measure ratios for every type of heating function (i.e. uniform, all $\alpha$ and all $\beta$), but for only those runs where $t_N=3000$ s. Note that we choose to only show results for five values of $t_N$ for aesthetic purposes.

@@

	\par Above $T_m$, higher temperatures arise when a power-law distribution of energy is assumed than for a nanoflare train with uniform heating rates. However, no information about the presence of a waiting time survives. Higher observed temperatures also arise for the single-fluid and electron heating cases where a ``hot shoulder'' can occur in $\mathrm{EM}(T)$ at $T\sim10$ MK. This is compared to the ion heating case where a finite equilibration time means that the electrons are heated more slowly. We find that, unlike some of the examples in \citetalias{barnes_inference_2016-1}, NEI is not a major consideration, a constant nanoflare train being the exception.

>>>>

%Define new commands as needed
\newcommand{\ang}{\AA~}
\defcitealias{barnes_inference_2016}{Paper I}
\renewcommand{\sectionautorefname}{Section}
\renewcommand{\subsectionautorefname}{Subsection}
%Set tikz options
\tikzstyle{box} = [rectangle, rounded corners, text centered, draw=black]
\tikzstyle{ghost} = [rectangle, rounded corners, text centered, draw=white]
\tikzstyle{arrow} = [thick, ->, >=stealth]

@@

	\par An analogous approach can be used to investigate the properties of the ``hot" coronal component expected from nanoflare heating, and is the subject of the present series of papers. In \citet{barnes_inference_2016} \citepalias[hereafter]{barnes_inference_2016}, we looked at the hot plasma properties due to a single isolated nanoflare. The effects of heating pulse duration, changes to conductive cooling due to heat flux limiting, differential heating of electrons and ions, and non-equilibrium ionization (NEI) were studied. It was shown that signatures of nanoflare heating are likely to be found in the temperature range $4\lesssim T\lesssim 10$ MK. The prospect of measurable signatures above $10$ MK was found to be diminished for short heating pulses (with duration $<100$ s), NEI, and differential heating of the ions rather than the electrons. It is important to stress for a single nanoflare that while the ``hot'' plasma is present, it cannot actually be detected.

@@

	\par In order to treat the evolution of the electron and ion populations separately, we use a modified version of the usual EBTEL equations. This amounts to computing spatial averages of the two-fluid hydrodynamic equations over both the transition region and corona\footnote{The two-fluid EBTEL  code is freely available and can be downloaded at: \url{https://github.com/rice-solar-physics/ebtelPlusPlus}.}. A full description and derivation of these equations can be found in Appendix B of \citetalias{barnes_inference_2016}. The relevant two-fluid pressure and density equations are,

@@

	where $c_2=\bar{T}_e/T_{e,a}\approx0.9$, $c_3=T_{e,0}/T_{e,a}\approx0.6$, $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency, and $\psi_{TR}$ is a term included to maintain charge and current and neutrality. Additionally, $c_1=\mathcal{R}_{TR}/\mathcal{R}_C$ and its formulation is discussed in \citet{cargill_enthalpy-based_2012} with additional modifications detailed in Appendix A of \citetalias{barnes_inference_2016}. These equations are closed by the equations of state $p_e=k_BnT_e$ and $p_i=k_BnT_i$. In the cases where we treat the plasma as a single-fluid, we use the original EBTEL model as described in \citet{klimchuk_highly_2008,cargill_enthalpy-based_2012}.

@@

	\par The loop is heated by a prescribed heating function, applied to either the electrons ($\bar{Q}_e$) or the ions ($\bar{Q}_i$). Both species cool through a combination of thermal conduction ($F_{ce,0},\,F_{ci,0}$) and an enthalpy flux to the lower atmosphere, with the electrons also undergoing radiative cooling ($\mathcal{R_C}$). In the case of conductive cooling, a flux limiter, $F_s=(1/2)fnk_BTV_e$, is imposed to mitigate runaway cooling in a low-density, high-temperature plasma. In all cases we use a saturation limit of $f=1$. See \citetalias{barnes_inference_2016} for a discussion of how $f$ is likely to effect the presence of hot emission in a nanoflare-heated plasma.

@@

	\par When considering the role of nanoflares in the production of hot plasma in AR cores, it is important to take non-equilibrium ionization (NEI) into account \citep{bradshaw_explosive_2006,reale_nonequilibrium_2008,barnes_inference_2016}. In a steady heating scenario, the ionization state is an adequate measure of the electron plasma temperature. Because the heating timescale is long (effectively infinite), the ionization state has plenty of time to come into equilibrium with the electron temperature.

@@

	\par As in \citetalias{barnes_inference_2016}, we use the numerical code\footnote{This code has been made freely available by the author and can be downloaded at: \url{https://github.com/rice-solar-physics/IonPopSolver}.} outlined in \citet{bradshaw_numerical_2009} to asses the impact of NEI on our results. Given a temperature and density profile from EBTEL, we compute the non-equilibrium ionization states for Fe IX through XXVII and the corresponding effective electron temperature, $T_{eff}$, that would be inferred by assuming ionization equilibrium. Using $T_{eff}$, we are then able to compute a corresponding NEI emission measure distribution, $\mathrm{EM}(T_{eff})$.

@@

	\par We now show the results of our nanoflare train simulations for each point in our multidimensional parameter space: species heated (single-fluid, electron or ion), power-law index ($\alpha$), waiting time ($t_N$), and waiting-time/event energy relationship ($\beta$). In each 0D hydrodynamic simulation, a loop of half-length $L=40$ Mm is heated by $N$ triangular events of duration $\tau=200$ s and peak heating rate $H_i$ for a duration of $t_{total}=8\times10^4$ s. The average interval between subsequent events is $t_N$ (in the uniform and $\beta=0$ cases, $t_{N,i}=t_N$ exactly for all $i$). We focus primarily on the emission measure distribution, $\mathrm{EM}(T)$, and observables typically calculated from $\mathrm{EM}(T)$. In all cases, the coronal emission measure is calculated according to the method outlined in section 3 of \citetalias{barnes_inference_2016}. The corresponding NEI results, $\mathrm{EM}(T_{eff})$, are calculated similarly, but using $T_{eff}$ (see \autoref{subsec:nei}) instead of $T$.

@@

	\par We compare $\mathrm{EM}(T)$ for three different types of heating functions, across a sample of six different heating frequencies. \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} show the emission measure distributions for the single-fluid, electron heating, and ion heating cases respectively. Each panel corresponds to a different average waiting time ($t_N$) and includes three different types of heating functions: uniform heating events (red), events chosen from a single power-law distribution of index $\alpha=-2.5$ with constant waiting time ($\beta=0$ case, blue), and a waiting time that depends on the energy released in the preceding event ($\beta=1$ case, green). The dashed lines denote the corresponding NEI cases, $\mathrm{EM}(T_{eff})$. The cases shown in \citetalias{barnes_inference_2016} correspond approximately to the red curves in the lower right panels ($t_N=5000$ s) in each of the three figures since the loop is allowed to cool and drain completely before reheating and a single nanoflare energy is used.

@@

	\par The behavior of $\mathrm{EM}(T)$ above $T_m$ is more complicated, but because $\mathrm{EM}(T_m)$ and $T_m$ are the same for all parameters, we can make a meaningful comparison between the different heating models. For the single-fluid model and short $t_N$, the emission measure distribution falls off sharply on the hot side for a uniform nanoflare train, but choosing heating events from a power law leads to a broader distribution. This just reflects the different initial temperatures generated with a power-law distribution since $T \simeq H^{2/7}$, where $H$ is the heating rate. As $t_N$ increases, the distribution for uniform heating gradually broadens as the initial temperature rises due to the lower density in which the heating occurs. A similar broadening occurs for power law heating distributions with the $\beta=0$ and $\beta=1$ results showing little difference. Note that the $\beta=0$ curve is barely visible as it overlaps almost completely with the $\beta=1$ curve. Especially interesting in this case are the results with NEI included. For a uniform nanoflare train, NEI plays no role up to $t_N$ = 2500 sec, but above that it restricts the temperatures that can be detected, as shown in \citetalias{barnes_inference_2016}. This hot emission is relocated to cooler temperatures, resulting in a small ``bump'' in the emission measure distribution near 10 MK. On the other hand, NEI plays almost no role in the power-law distributions, for either the $\beta=0$ or $\beta=1$ cases.

@@

	\par When only the ions are heated (\autoref{fig:ion_em}), for intermediate to low heating frequencies (i.e. $t_N\ge1500$ s), $\mathrm{EM}(T)$ in the uniform heating case is truncated below 10 MK and in the power law cases extends to just above 10 MK for the longest waiting time ($t_N=5000$ s). This cutoff at lower temperatures is due to the fact that the electrons cannot ``see'' the ions until they have cooled well below their peak temperature. This is discussed in \citetalias{barnes_inference_2016} though in the single-pulse cases, the cutoff occured at lower temperatures. Additionally, in both the uniform and power law cases, the peak of $\mathrm{EM}(T)$ is wider for these low frequencies compared to those shown in the lower right panels of \autoref{fig:single_em} and \autoref{fig:el_em}. NEI now plays no role in any of the cases.

@@

	\par In \citet{cargill_active_2014}, \citetalias{barnes_inference_2016}, and \autoref{subsec:em_dist}, we have suggested that the plasma density prior to the nanoflare occuring is a crucial parameter in determining the emission measure distribution. This arises in two distinct ways. Below $T_m$, the temperature and density at which the nanoflare occurs cuts off the emission at lower temperatures. When combined with an energy-dependent waiting time, this can lead to a range of EM slopes in this region \citep{cargill_active_2014}. Above $T_m$, the initial density determines the temperature increase due to the nanoflare, how quickly the initial hot plasma cools, and whether NEI effects are important. We now examine this further.

@@

	\par Our results here suggest that while $a$ is an adequate parameter for describing the cool side of $\mathrm{EM}(T)$, the functional form $\mathrm{EM}\sim T^{-b}$ does not adequately capture the character of the hot part of $\mathrm{EM}(T)$ over any reasonable temperature range. \citet{antiochos_evaporative_1978} showed analytically that accounting for evaporative cooling and assuming constant pressure gives $b=11/2$, though this value can be as low as $b=5/2$ if a flux limiter is included. However, in \citetalias{barnes_inference_2016}, we showed that in the case of a single 200 s nanoflare that heats only the electrons, the assumption of constant electron pressure during the heating and early conductive cooling phases does not hold. Our results here are consistent with our findings in \citetalias{barnes_inference_2016} in that the parameter $b$ does not provide any valuable information about $\mathrm{EM}(T)$ for $T>T_m$ when two-fluid effects are considered. Clearly, an alternative metric for measuring the amount of hot plasma in the emission measure distribution is needed.

@@

	\authorcomment1{TODO:Change/update all temperatures ratio references appropriately. TODO: add additional figure/paragraph describing how changes in hot/cool temperatures are likely to affect our result}

@@

		\par\citet{brosius_pervasive_2014} proposed another possible diagnostic for the hot non-flaring corona. Using observations of an active region from the \textit{EUNIS-13} sounding rocket, they found that the intensity ratio of Fe XIX (formed at $T\approx8.9$ MK) to Fe XII (formed at $T\approx1.6$ MK) is $\sim0.59$ inside the AR core as compared to $\sim0.076$ outside. They argue that this provides possible evidence for impulsive heating. This arises from the fact that the $\mathrm{EM}(T)$ distribution resulting from low- and intermediate-frequency nanoflares is dual-valued as a function of temperature \citep[see \autoref{fig:single_em}-\autoref{fig:ion_em} and][]{cargill_implications_1994}. For example, in the lower right panel of \autoref{fig:single_em}, $\mathrm{EM}\approx 10^{26.5}$ cm$^{-5}$ at $T = 1.6$ MK and $8.9$ MK. This suggests that the approach of \citet{brosius_pervasive_2014} could be used for any pair of appropriate emission lines and is likely to be of particular use where very limited spectral coverage is available either above or below $T_m$. Indeed for impulsive heating of any kind, the generic $\mathrm{EM}(T)$ curve remains similar (though not identical) as the magnitude of the heating changes. For flare-like energy release one would expect the hot emission to be much greater than the cold emission, with the opposite in the quiet Sun.

	\par We define a general emission measure ratio, $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$ and \textbf{for this paper consider $T_{hot}=10^{6.942}$ K and $T_{cool}=10^{6.187}$ K, the formation temperatures of Fe XIX and XII, respectively \citep[i.e. the temperature $T$ which maximizes the contribution function $G_{\lambda}(T)$ calculated using CHIANTI v8,][]{dere_chianti_1997,del_zanna_chianti_2015}}. This also provides a way to compare in a concise way every point in our multidimensional parameter space though we acknowledge that we are reducing $8\times10^4$ s of loop evolution to a single value. This ratio is shown in \autoref{fig:em_ratio_hist_single}, \autoref{fig:em_ratio_hist_el}, and \autoref{fig:em_ratio_hist_ion} for the single-fluid model, electron and ion heating, respectively. In the left-hand panels each individual histogram (denoted by linestyle and color) corresponds to a different type of heating function. This means, for example, that the solid blue histogram includes emission measure ratios for all values of $t_N$, but for only those cases where heating events are chosen from a power-law distribution of $\alpha=-1.5$ and $t_{N,i}=t_N$ for all $i$ (i.e. $\beta=0$). The right panels show these same emission measure ratios, but now categorized by $t_N$. For example, the solid red histogram includes emission measure ratios for every type of heating function (i.e. uniform, all $\alpha$ and all $\beta$), but for only those runs where $t_N=3000$ s. Note that we choose to only show results for five values of $t_N$ for aesthetic purposes.

@@

	\par Above $T_m$, higher temperatures arise when a power-law distribution of energy is assumed than for a nanoflare train with uniform heating rates. However, no information about the presence of a waiting time survives. Higher observed temperatures also arise for the single-fluid and electron heating cases where a ``hot shoulder'' can occur in $\mathrm{EM}(T)$ at $T\sim10$ MK. This is compared to the ion heating case where a finite equilibration time means that the electrons are heated more slowly. We find that, unlike some of the examples in \citetalias{barnes_inference_2016}, NEI is not a major consideration, a constant nanoflare train being the exception.
